---
title: "Smoke and Die"
author: "Leanne (Yuen Wan) Lee, Yeonghwan Son (Tony)"
date: "December 7, 2015"
output: pdf_document
---

```{r echo = FALSE}
library(knitr)
library(readr)
library(ggplot2)
read_chunk("smoke.R")
```

The causal relation between cigarette smoking and lung cancer have been a field of wide interest and extensive research for many existing organizations and individuals. In this particular project, we plan to establish the relationship between cigarette smoking and lung cancer. 
Furthermore, we look into other factors that could affect one's chance of being diagnozed with lung cancer such as one's age, race and gender.

To begin with, we compare the population of cigarette smokers and the number of lung cancer patients in each of the 51 states in the United States of America.

## Downloading Raw Data
```{r chunk1, eval = FALSE}
```

## Data Cleaning and Preparation
```{r chunk2}
```

## Basic Clean Data Inspection
Looking into the data frame 'smoke_cdf'
```{r chunk3}
```

Inspecting the data frame 'lung_cancer_cdf'
```{r chunk4}
```

Merging the two data frames 'smoke_cdf' and 'lung_cancer_cdf' to obtain 'smoke_cancer_cdf' for future use.
Then, using 'smoke_cancer_cdf', we look for the state with the highest percentage of cigarette smoking population.
```{r chunk5}
```

Looking for the state with the lowest percentage of cigarette smoking population.
```{r chunk6}
```

Looking for the state with the highest percentage of lung cancer patients.
```{r chunk7}
```

Looking for the state with the lowest percentage of lung cancer patients.
```{r chunk8}
```

## Visual Analysis Part 1

The first graph we introduce is a barplot of the percentage of cigarette smoking population in each state. 
The bars of the plot are arranged in an ascending order of the percentage. 
We observe from the graph, as we have inspected above, Utah has the lowest and West Virginia has the highest percentage of cigrette smoking population. 
```{r chunk9}
```

Then next graph is a similar barplot as the previous one, but it shows the percentage of lung cancer patients in each state. 
We see that Utah, which had the lowest smoking population percentage, also has the lowest percentage of lung cancer patients among all the states. Kentucky has has the highest rate of lung cancer patients followed by West Virginia which had the highest cigarette smoking population percentage.
```{r chunk10}
```

To compare the two data sets introduced in the two previous graphs, 
```{r chunk11}
```

In this linear regression model, we analyzed the correlation 
between the rate of smoking population with the number of lung 
cancer patients. It clearly show that there is a positive 
correction between the two factors.
```{r chunk12}
```

## Downloading male and female lung cancer raw data
```{r chunk13, eval = FALSE}
```

## Data Cleaning and Preparation for lung cancer data
```{r chunk14}
```

Data preparation for plotting lung cancer rate vs race
```{r chunk15}
```

## Visual Analysis Part 2 

In this bar chart, it illustrates that the rate of lung cancer patients
by race. It shows that black male and white female have higher 
chances of getting lung cancer.
```{r chunk16}
```

In this bar chart, it shows relationship between the rate of lung cancer 
patients by different age groups. The graph not only shows that older people have higher chance of being diagnosed with lung cancer, but also males have higher chance of getting lung cancer than females do. 
```{r chunk17}
```

#Exporting plots as png files
```{r chunk18, eval = FALSE}
```
