---
title: "smoke_and_die"
author: "Leanne Lee, Yeonghwan Son (Tony)"
date: "December 7, 2015"
output: pdf_document
---

```{r echo = FALSE}
library(knitr)
library(readr)
library(ggplot2)
read_chunk("smoke.R")
```

## Downloading Raw Data
```{r chunk1}
```

## Data Cleaning and Preparation
```{r chunk2}
```

## Basic Clean Data Inspection
Inspection for smoking population
```{r chunk3}
```

Inspection for lung cancer rate
```{r chunk4}
```

Combine smoking population data frame and lung cancer rate data frame
```{r chunk5}
```

The state with the lowest smoking population rate
```{r chunk6}
```

The state with the highest lung cancer rate
```{r chunk7}
```

The state with the lowest lung cancer rate
```{r chunk8}
```

#Visualization
In the graph of smoker population in USA by state,
```{r chunk9}
```

```{r chunk10}
```

```{r chunk11}
```

```{r chunk12}
```

## Downloading male and female lung cancer raw data
```{r chunk13}
```

## Data Cleaning and Preparation for lung cancer data
```{r chunk14}
```

Data preparation for plotting lung cancer rate vs race
```{r chunk15}
```

## Visualization 
```{r chunk16}
```

```{r chunk17}
```

#Export the images
```{r chunk18}
```
