---
title: "Smoke And Die"
author: "Leanne (Yuen Wan) Lee, Yeonghwan Son (Tony)"
date: "December 7, 2015"
output: pdf_document
---

```{r echo = FALSE}
library(knitr)
library(readr)
library(ggplot2)
read_chunk("smoke.R")
```

## Downloading Raw Data
```{r chunk1, eval = FALSE}
```

## Data Cleaning and Preparation
```{r chunk2}
```

## Basic Clean Data Inspection
Inspection for smoking population
```{r chunk3}
```

Inspection for lung cancer rate
```{r chunk4}
```

Combine smoking population data frame and lung cancer rate data frame
```{r chunk5}
```

The state with the lowest smoking population rate
```{r chunk6}
```

The state with the highest lung cancer rate
```{r chunk7}
```

The state with the lowest lung cancer rate
```{r chunk8}
```

#Visualization Part 1

In the graph of "Smoker Population in USA by State", 
we ordered the percentage of smokers in ascending order by states.
It shows that West Virginia has the highest percenatge of smokers
and Utah has the lowest percentage of smoking across the United States.
```{r chunk9}
```

In the graph of "Lung Cancer Patients in USA by State",
we ordered the percentage of lung cancer patients in ascending 
order by states. It shows that Kentucky has the highest lung 
cancer rate while Utah has teh lowest lung cancer rate.
```{r chunk10}
```

In this graph, we compared the rate of smoking population of each
state with the rate of lung cancer patients. It shows that the higher
smoking population in the state lead to a greater number of lung 
cancer patients.
```{r chunk11}
```

In this linear regression model, we analyzed the correlation 
between the rate of smoking population with the number of lung 
cancer patients. It clearly show that there is a positive 
correction between the two factors.
```{r chunk12}
```

## Downloading male and female lung cancer raw data
```{r chunk13, eval = FALSE}
```

## Data Cleaning and Preparation for lung cancer data
```{r chunk14}
```

Data preparation for plotting lung cancer rate vs race
```{r chunk15}
```

## Visualization Part 2 

In this bar chart, it illustrates that the rate of lung cancer patients
by race. It shows that black male and white female have higher 
chances of getting lung cancer.
```{r chunk16}
```

In this bar chart, it shows relationship between the rate of lung cancer 
patients by different age groups. The graph not only shows that older people have higher chance of being diagnosed with lung cancer, but also males have higher chance of getting lung cancer than females do. 
```{r chunk17}
```

#Exporting plots as png files
```{r chunk18}
```
